Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-05-30 paper/paper.qmd
Add 95th pct table to paper

---
title: "Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome"
bibliography: references.bib
fontsize: 11pt
date: last-modified
date-format: medium
format:
  manuscript-pdf:
    mainfont: Helvetica
    keep-tex: true
    linenumbers: true
    doublespacing: true
    lof: false
  html:
    embed-resources: true
runningtitle: Predicting CDI Severity from OTUs
runningauthor: Sovacool
papertype: Preprint
author:
  - name: Kelly L. Sovacool
    orcid: 0000-0003-3283-829X
    affiliations:
      - ref: bioinf
  - name: Sarah E. Tomkovich
    affiliations:
      - ref: micro
  - name: Megan L. Coden
    affiliations:
      - ref: mcdb
  - name: Vincent B. Young
    affiliations:
      - ref: micro
      - ref: intmed
  - name: Krishna Rao
    affiliations:
      - ref: intmed
  - name: Patrick D. Schloss
    orcid: 0000-0002-6935-4275
    email: pschloss@umich.edu
    corresponding: true
    affiliations:
      - ref: micro
      - ref: ccmb
affiliations:
  - id: bioinf
    name: Department of Computational Medicine & Bioinformatics, University of Michigan
  - id: micro
    name: Department of Microbiology & Immunology, University of Michigan
  - id: mcdb
    name: Department of Molecular, Cellular, and Developmental Biology, University of Michigan
  - id: intmed
    name: Division of Infectious Diseases, Department of Internal Medicine, University of Michigan
  - id: ccmb
    name: Center for Computational Medicine and Bioinformatics, University of Michigan
abstract: TODO
importance: TODO
keywords: _C. difficile_ infection, supervised machine learning, gut microbiome, amplicion sequencing
---

```{r load_data, message = FALSE}
library(here)
library(tidyverse)

@@

@@

>>>>

---
title: "Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome"
bibliography: references.bib
fontsize: 11pt
date: last-modified
date-format: medium
format:
  manuscript-pdf:
    mainfont: Helvetica
    keep-tex: true
    linenumbers: true
    doublespacing: true
    lof: false
  html:
    embed-resources: true
runningtitle: Predicting CDI Severity from OTUs
runningauthor: Sovacool
papertype: Preprint
author:
  - name: Kelly L. Sovacool
    orcid: 0000-0003-3283-829X
    affiliations:
      - ref: bioinf
  - name: Sarah E. Tomkovich
    affiliations:
      - ref: micro
  - name: Megan L. Coden
    affiliations:
      - ref: mcdb
  - name: Vincent B. Young
    affiliations:
      - ref: micro
      - ref: intmed
  - name: Krishna Rao
    affiliations:
      - ref: intmed
  - name: Patrick D. Schloss
    orcid: 0000-0002-6935-4275
    email: pschloss@umich.edu
    corresponding: true
    affiliations:
      - ref: micro
      - ref: ccmb
affiliations:
  - id: bioinf
    name: Department of Computational Medicine & Bioinformatics, University of Michigan
  - id: micro
    name: Department of Microbiology & Immunology, University of Michigan
  - id: mcdb
    name: Department of Molecular, Cellular, and Developmental Biology, University of Michigan
  - id: intmed
    name: Division of Infectious Diseases, Department of Internal Medicine, University of Michigan
  - id: ccmb
    name: Center for Computational Medicine and Bioinformatics, University of Michigan
abstract: TODO
importance: TODO
keywords: _C. difficile_ infection, supervised machine learning, gut microbiome, amplicion sequencing
---
```{rsetup, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(dpi = 600)
```
```{r load_data, message = FALSE}
library(here)
library(knitr)
library(tidyverse)

@@

prevalance of cdi. prevalance of severe cdi outcomes.

@@

table of NNS at 95th pct of risk for each outcome x dataset (@tbl-risk).

```{r risk_95th_pct_decision_thresholds, message=FALSE}
#| label: tbl-risk
#| tbl-cap: "**Predive model performance at 95th percentile of risk.**"
read_csv(here('results','decision_thresholds.csv')) %>% kable()
```
